---
title: "Introduction to StatComp20030"
author: "Wenyi Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp20030}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Overview

__StatComp20030__ is a simple R package, which is used for simple hypothesis testing, interval estimation and random number generation. Two functions are considered, namely, _laplace.randnum_ (generate random nubers for Laplace distribution) and _sigma.test_ (variance hypothesis test and interval estimation for single normal population)


## Exhibition _sigma.test_ and _laplace.randnum_

When the variance of a single normal population needs to be tested and interval estimated, we can use _sigma.test_ function to judge the unilateral hypothesis and bilateral hypothesis of variance, and generating estimators of  confidence intervals.
The source R code for _sigma.test_ is as follows:
```{r,eval=FALSE}
sigma2test<-function(x,mu,sigma,hypothesis,a){
  n=length(x)
  s2=var(x)
  
  if(hypothesis=='equal'){
    interl=(n-1)*s2/qchisq(1-(a/2),n-1)
    interr=(n-1)*s2/qchisq(a/2,n-1)
    inter=c(interl,interr)
    c=(n-1)*s2/sigma^2
    if(c>qchisq(a/2,n-1)&&c<qchisq(1-(a/2),n-1))
      AoR='accept'
    else AoR='reject'
    result=list('original hypothesis'=AoR,'interval estimation'=inter)
  }  
  if(hypothesis=='greater'){
    interl=(n-1)*s2/qchisq(1-(a/2),n-1)
    interr=(n-1)*s2/qchisq(a/2,n-1)
    inter=c(interl,interr)
    c=(n-1)*s2/sigma^2
    if(c<qchisq(a,n-1))
      AoR='reject'
    else AoR='accept'
    result=list('original hypothesis'=AoR,'interval estimation'=inter)
  }
  if(hypothesis=='less'){
    interl=0
    interr=(n-1)*s2/qchisq((1-a),n-1)
    inter=c(interl,interr)
    c=(n-1)*s2/sigma^2
    if(c>qchisq(1-a,n-1))
      AoR='reject'
    else AoR='accept'
    result=list('original hypothesis'=AoR,'interval estimation'=inter)
  }
  return(result) 
}
```



When generating the random numbers of the laplace distribution,  we can use function _laplace.randnum_ ,here is an example to use the function to draw a density histogram.
The source R code for  we can use _laplace.randnum_ is as follows:
```{r,eval=FALSE}
laplacerandnum<-function(n,beta,mu){
  u<-runif(n)
  x<-numeric(n)
  for (i in 1:n){
    if(u[i]>=0.5)
      x[i]<-mu-beta*log(1-u[i])
    else
      x[i]<-mu+beta*log(u[i])
  }
  return(x)
}

```






